\begin{basicSection}{Work Experience}
    \begin{workExperienceSection}{Allstate}{Jun 2021 - Present}{Lead Full-Stack Software Engineer}{Charlotte, NC - Home Based}
        \begin{workExperienceSectionSubSection}{Responsibilities}
            \item Lead and mentor a team of software engineers with an aim to promote individual growth and improve overall team performance.
            \item Lead Agile XP ceremonies such as iteration planning, stand-up, sprint review, and retrospectives.
            \item Ensure products meet operational readiness standards by maintaining high level architectural documentation, coordinating with product owners and systems engineering, configuring application monitoring and alerting, creating disaster recovery plans, and more.
            \item Participate in pair programming sessions daily to ensure code quality, improve team cohesion, and mentor team members.
            \item Embrace test driven development (TDD) to reduce bugs and errors in the final product.
            \item Facilitate technical planning sessions that result in "just good enough documentation" of high level architectures and design patterns.
            Additionally, share knowledge of the UML standard to ensure that engineers have a common design language.
            \item Create and maintain CI/CD pipelines using Jenkins and Docker.
            \item Maintain and contribute to inner-sourced Java and React libraries used by multiple production applications within the organization.
        \end{workExperienceSectionSubSection}
        \begin{workExperienceSectionSubSection}{Accomplishments}
            \item Created an internally sourced user testing platform that manages and distributes fake customer data in a way the is safe for downstream systems.
            Additionally, the platform collects metrics and actionable feedback during testing sessions and facilitates its delivery to application teams.
            (ReactJs, SpringBoot, MSSQL)
            \item Utilized event-driven and microservice architectures to deliver an enterprise communication management system.
            (SpringBoot, MSSQL, ReactJs, Apache Kafka)
            \item Led the production of an ETL PoC that demonstrated the ability to automatically accumulate messages from any Kafka topic within the organization and deliver them to a data lake.
            (Apache Kafka, Kafka Connect, SpringBoot)
            \item Engineered a declarative decision modeling platform for data scientist them to create low to no code programs via a visual DAG editor.
            Made heavy use of graph theory and traversal algorithms to determine when specific execution context is available.
            (ReactJs, SpringBoot, BPMN)
        \end{workExperienceSectionSubSection}
    \end{workExperienceSection}
    \begin{workExperienceSection}{CorrChoice}{Aug 2017 - Jun 2021}{Application Developer}{Concord, NC}
        \begin{workExperienceSectionSubSection}{Responsibilities}
            \item Develop custom software solutions and integrations based on company and customer needs.
            \item Troubleshoot, maintain, and develop PLC programs for over 30 different pieces of equipment.
        \end{workExperienceSectionSubSection}
        \begin{workExperienceSectionSubSection}{Accomplishments}
            \item Planned, managed, and developed a B2B native mobile application that includes a Node.js REST API, React Native mobile application, and React internal dashboard.
            Set up efficient CI/CD pipelines that automatically build and release new application builds to the Google and Apple app stores.
            (Node.js, Socket.io, ReactJs, React Native, Azure Pipelines)
            \item Created a quality management system that implements a Django REST API and React front-end.
            (ReactJs, Django, MySQL, RPYC, Progress OpenEdge)
            \item Improved shipping lane crossing safety in a production facility by developing a web socket-based application used to request and signal pedestrian crossing.
            (Node.js, Socket.io, JQuery, Python)
        \end{workExperienceSectionSubSection}
    \end{workExperienceSection}
    \begin{workExperienceSection}{United States Marine Corps}{Aug 2013 - Aug 2017}{Squad Leader}{Jacksonville, NC}
        \item Effectively led a team of 12 individuals in high stress situations.
    \end{workExperienceSection}
\end{basicSection}